---
title: "AACR GENIE data access"
author: "Laura Cosgrove"
date: "2/21/2019"
output: github_document
---

## Getting Data

```{r}
library(tidyverse)
#install.packages("synapser", repos=c("https://sage-bionetworks.github.io/ran", "http://cran.fhcrc.org"))
library(synapser)
```

Put your login info here
```{r eval=FALSE}
#synLogin("laura_cosgrove", "")
```

Download text files

```{r eval=FALSE}
data_CNA <- synGet("syn17394020", downloadLocation="./data/")

data_clinical_patient <- synGet("syn17394024", downloadLocation="./data/")

data_clinical_sample <- synGet("syn17394030", downloadLocation="./data/")

data_fusions <- synGet("syn17394035", downloadLocation="./data/")

data_guide <- synGet("syn17394098", downloadLocation="./data/")

data_mutations_extended <- synGet("syn17394041", downloadLocation="./data/")

```

Read text files to CSV and save to RData the ones you want to use (bc very big)

```{r eval=FALSE}
data_CNA <- read.delim("./data/data_CNA_5.0-public.txt")

data_mutations <- read.delim("./data/data_mutations_extended_5.0-public.txt", skip = 1) 

saveRDS(data_mutations, "data_mutations.rds")
```

## Initial Exploration

Just looked at mutations so far.

```{r}
data_mutations <- readRDS("data_mutations.rds")
data_mutations <- data_mutations %>% 
  as_tibble() 

glimpse(data_mutations)

```

There's one potential response variable - Clinical Significance. Let's examine that more closely:

```{r, fig.height=10, fig.width=12}
data_mutations %>% 
  group_by(CLIN_SIG) %>% 
  summarize(count = n()) %>% 
  filter(!CLIN_SIG == "") %>% #Count of 404077 dropped
  mutate(clin_sig = forcats::fct_reorder(CLIN_SIG, count)) %>% 
  top_n(30) %>% 
  ggplot(aes(x = clin_sig, y = count)) +
  geom_col() +
  geom_text(aes(label = count), hjust = -0.1, size = 3) +
  coord_flip() + 
  labs(title = "Clinical Significance of Mutations") +
  ggthemes::theme_fivethirtyeight()

```

There's a lot of missing data (404,077 obs) and the vast majority of what's remaining is coded either pathogenic or uncertain, and then a lot of multiple-coded values. Maybe not worth looking at this as a response.